---
title: "Webscaping"
author: "Rick"
date: '2019-01-06'
output: html_document
---
## Credit to YouTuber: R4DS Online Learning Community (https://www.youtube.com/watch?v=0mvlZhYk44E)

# Load libraries

* Tidyverse for all the tidy packages
* rvest to "harvest" all the data from the web

```{r, message=FALSE}
library(tidyverse) # ggplot, dplyr, tidyr, readr, purrr, tibble, stringr, forcats
library(rvest) # interacting with html and webcontent
library(glue) # used to combine strings in clever ways
```

## Data Sourcing

we want to source NFL positional salaries to match the
[538 article](https://fivethirtyeight.com/features/running-backs-are-finally-getting-paid-what-theyre-worth/).

we dont have access to NFL salaries from ESPN, so we have to find it manually at sportrac

```{r}
url <- "https://www.x-rates.com/table/?from=USD&amount=1"

read_html(url) %>%
  html_nodes("table") %>%
  html_table()
```

## Finding the specific table path
* Inspect the web page to find what the path is

```{r}
read_html(url) %>%
  html_nodes("#content > div:nth-child(1) > div > div.col2.pull-right.module.bottomMargin > div.moduleContent > table:nth-child(4)") %>%
  html_table()
```

## Save as a dataframe

* Read html from url, aim html_table() at the path and save to dataframe

```{r}
curr_rate <- read_html(url) %>%
  html_node("#content > div:nth-child(1) > div > div.col2.pull-right.module.bottomMargin > div.moduleContent > table:nth-child(4)") %>%
  html_table()

# Take a peak at the data
glimpse(curr_rate)

# How many dataframes?
# some number
```


## Building a web scrapping function

```{r}
url <- "https://www.x-rates.com/table/?from=USD&amount=1"

# things we want to change "from" ("country") and "amount"

base_url <- "https://www.x-rates.com/table/"

currency_scrape <- function(country, amount) {
  
  url <- glue("https://www.x-rates.com/table/?from={country}&amount={amount}")
  
  read_html(url) %>%
    html_node("#content > div:nth-child(1) > div > div.col2.pull-right.module.bottomMargin > div.moduleContent >     table:nth-child(4)") %>%
    html_table()
}

# check
currency_scrape("JPY", 1)
```

## Build up inputs as scaffold

*currency (1)
*countries (USD, ZAR, SGD, NZD, MYR, JPY, INR, HKD, EUR, CAD, GBP, AUD)

```{r}
# currency is 1
currency <- 1

# Countries
countries <- c("USD", "CAD", "JPY", "EUR", "ZAR", "SGD", "NZD", "MYR", "INR", "HKD", "GBP", "AUD")

scaffold <- tibble(country = list(countries),
                   amount = currency) %>% tidyr::unnest()
scaffold
```

## Test inputs

```{r}
currency_scrape("USD", 1)
```

## Using the scaffold to build a dataframe

```{r}
# Limit to first four rows of our scaffold dataframe
head(scaffold, 4)

# Create dataframe with map2
tbl_data <- head(scaffold, 4) %>%
  mutate(data = purrr::map2(country, amount, ~currency_scrape(.x, .y)))

# Check the data
tbl_data

# Look at the nested dataframe contents
tbl_data$data

# Remove the NA column and merge into a continuous dataframe
tbl_data$data %>% purrr::flatten_df()
```

## Rebuild our function
* Goal is to move table data into data column
* But we need to flatten this data into a combined dataframe
* Also know that dataframes will end up nested

```{r}

currency_scrape <- function(country, amount){
  
  Sys.sleep(3)
  
  cat(".")
  
  url <- glue("https://www.x-rates.com/table/?from={country}&amount={amount}")
  
  read_html(url) %>%
    html_nodes("#content > div:nth-child(1) > div > div.col2.pull-right.module.bottomMargin > div.moduleContent >     table:nth-child(4)") %>%
    html_table() %>%
    purrr::flatten_df() %>%
    set_names(c("Country", "Currency", "Inv. Currency"))
}


# Run this. (It will take some time)
scraped_df <- scaffold %>%
  mutate(data = map2(country, amount, ~currency_scrape(.x, .y)))

# Let's look
scraped_df 
```

## Data cleanup

```{r}
position_group_df <- scraped_df %>%
  unnest()

position_group_df
```

## Saving the data

```{r}
saveRDS(position_group_df, file = "x-rate_currency.RDS")
```

## Arrange data for plotting

```{r}
# Make dataframe for the plot
mean_currency_df <- position_group_df %>%
  group_by(amount, country) %>%
  top_n(16, Currency) %>%
  summarize(avg_currency = mean(Currency))

mean_currency_df
```

## Plot of average currency

```{r}
ggplot(mean_currency_df, aes(x = countries, y = avg_currency)) + 
         geom_line() +
         geom_point() +
         ylim(0, 30)
```

## Create dataframe for original plot

```{r}
top16_currency_df <- position_group_df %>%
  group_by(amount, country) %>%
  top_n(16, Currency) %>%
  ungroup()

top16_currency_df
```

## Create and save the plot

```{r}
(g1 <- ggplot(top16_currency_df, aes(x = country, y = Currency)) +
  geom_point(alpha = .3, size = 3) +
  geom_smooth(color = "orangered",
              se = FALSE) +
  scale_y_continuous(limits = c(0, 30),
                     breaks = seq(0, 30, 5),
                     labels = c("0", "5", "10", "15", "20", "25", "$30")) +
  labs(title = "Average Currency for Top Countries",
       subtitle = "Top 16 Currencies",
       y = "Average Currency Value", x = "Country",
       caption = "\nGraphic: Rick_Ys | Data: x-rates.com"))

ggsave("Avg_currency_rate.png", g1, height= 8, width = 10, units = "in", dpi = 600)
beepr::beep(4)
```














